Circumnuclear Media and Accretion Rates of Quiescent Supermassive Black Holes

### 2015-03-30 ms.tex
more changes to analytics
table now has solutions corresponding to the latest sigma prescription.

$    10^{ 6 }$ & 300 & 0.8 & 100 & 0.14 & $ 6.4 \times 10^{ -5 }$ & 17 \\
... & 600 & 0.8 & 100 & $ 3.4 \times 10^{ -2 }$ & $ 1.1 \times 10^{ -5 }$ & $ 1.6 \times 10^{ 3 }$ \\
... & 1200 & 0.8 & 100 & $ 8.2 \times 10^{ -3 }$ & $ 1.9 \times 10^{ -6 }$ & $ 7.2 \times 10^{ 4 }$ \\
$    10^{ 7 }$ & 300 & 0.8 & 25 & 0.65 & $ 3.9 \times 10^{ -4 }$ & 1.8 \\
... & ... & 0.8 & 50 & 0.65 & $ 3.9 \times 10^{ -4 }$ & $\mathbf{0.82}$ \\
... & ... & 0.8 & 100 & 0.83 & $ 5.2 \times 10^{ -4 }$ & $\mathbf{0.33}$ \\
... & ... & 0.8 & 200 & 0.91 & $ 5.9 \times 10^{ -4 }$ & $\mathbf{0.18}$ \\
... & ... & 0.8 & 400 & 2.3 & $ 1.8 \times 10^{ -3 }$ & $\mathbf{ 1.9 \times 10^{ -2 }}$ \\
... & 600 & 0.8 & 25 & $ 8.9 \times 10^{ -2 }$ & $ 3.6 \times 10^{ -5 }$ & $ 4.4 \times 10^{ 2 }$ \\
... & ... & 0.8 & 100 & $ 8.9 \times 10^{ -2 }$ & $ 3.6 \times 10^{ -5 }$ & $ 4.4 \times 10^{ 2 }$ \\
... & 1200 & 0.8 & 100 & $ 2.1 \times 10^{ -2 }$ & $ 6.4 \times 10^{ -6 }$ & $ 2.4 \times 10^{ 4 }$ \\
$    10^{ 8 }$ & 300 & 0.8 & 25 & 1.3 & $ 9.4 \times 10^{ -4 }$ & $\mathbf{1}$ \\
... & ... & 0.8 & 50 & 2.1 & $ 1.6 \times 10^{ -3 }$ & $\mathbf{0.19}$ \\
... & ... & 0.8 & 100 & 3.8 & $ 3.3 \times 10^{ -3 }$ & $\mathbf{ 2.2 \times 10^{ -2 }}$ \\
... & ... & 0.8 & 200 & 7.3 & $ 7.2 \times 10^{ -3 }$ & $\mathbf{ 2.1  \times 10^{ -3 }}$ \\
... & 450 & 0.8 & 100 & 0.72 & $ 4.4 \times 10^{ -4 }$ & 4 \\
...$^{\dagger}$ & ... & 0.8 & 100 & 3.3 & $ 2.8 \times 10^{ -3 }$ & $\mathbf{2.8}$\\
... & 600 & 0.8 & 25 & 0.26 & $ 1.3 \times 10^{ -4 }$ & $ 1.1 \times 10^{ 2 }$ \\
... & ... & 0.8 & 100 & 0.28 & $ 1.5 \times 10^{ -4 }$ & 76 \\
...$^{\dagger}$ & ... & 0.8 & 100 & 0.29 & $ 1.5 \times 10^{ -4 }$ &70 \\
...$^{\ddagger}$ & ... & 0.8 & 100 & 0.31 & $ 1.6 \times 10^{ -4 }$ & 73 \\
... & ... & 0.8 & 200 & 0.3 & $ 1.5 \times 10^{ -4 }$ & 67 \\
... & ... & 0.8 & 400 & 0.31 & $ 1.6 \times 10^{ -4 }$ & 58 \\
... & 1200 & 0.8 & 100 & $ 5.4 \times 10^{ -2 }$ & $ 2.0 \times 10^{ -5 }$ & $ 7.2 \times 10^{ 3 }$ \\

@@

$    10^{ 6 }$ & 600 & 0.1 & 25 & $ 9.9 \times 10^{ -2 }$ & $ 8.2\times 10^{ -6 }$ & 99 & Conv\\
... & ... & 0.1 & 50 & 0.34 & $ 8.5 \times 10^{ -5 }$ & $\mathbf{0.45}$ \\
... & 1200 & 0.1 & 25 & $ 1.7 \times 10^{ -2 }$ & $ 2.9 \times 10^{ -7 }$ & $ 1.4 \times 10^{ 5 }$ \\
... & ... & 0.1 & 50 & $ 1.7 \times 10^{ -2 }$ & $ 2.9 \times 10^{ -7 }$ & $ 1.4 \times 10^{ 5 }$ \\
... & ... & 0.1 & 100 & $ 1.7 \times 10^{ -2 }$ & $ 2.9 \times 10^{ -7 }$ & $ 1.4 \times 10^{ 5 }$ \\
$    10^{ 7 }$ & 600 & 0.1 & 25 & 0.24 & $ 4.3 \times 10^{ -5 }$ & 41 \\
... & ... & 0.1 & 50 & 0.57 & $ 2.3 \times 10^{ -4 }$ & $\mathbf{0.38}$ \\
... & 1200 & 0.1 & 25 & $ 4.4 \times 10^{ -2 }$ & $ 1.8 \times 10^{ -6 }$ & $ 2.2 \times 10^{ 4 }$ \\
... & ... & 0.1 & 50 & $ 4.7 \times 10^{ -2 }$ & $ 2.0 \times 10^{ -6 }$ & $ 1.7 \times 10^{ 4 }$ \\
... & ... & 0.1 & 100 & $ 5.3 \times 10^{ -2 }$ & $ 2.5 \times 10^{ -6 }$ & $ 9.8 \times 10^{ 3 }$ \\
$    10^{ 8 }$ & 600 & 0.1 & 25 & 0.39 & $ 1.1 \times 10^{ -4 }$ & 31 \\
... & ... & 0.1 & 50 & 0.66 & $ 3.0 \times 10^{ -4 }$ & 3 \\
... & ... & 0.1 & 100 & 2.6 & $ 4.0 \times 10^{ -3 }$ & $\mathbf{ 5.7 \times 10^{ -3 }}$ \\
... & 1200 & 0.1 & 25 & 0.1 & $ 8.4 \times 10^{ -6 }$ & $ 5.6 \times 10^{ 3 }$ \\
... & ... & 0.1 & 50 & 0.11 & $ 9.8 \times 10^{ -6 }$ & $ 4.0 \times 10^{ 3 }$ \\
... & ... & 0.1 & 100 & 0.12 & $ 1.2 \times 10^{ -5 }$ & $ 2.4 \times 10^{ 3 }$ \\
... & ... & 0.1 & 200 & 0.16 & $ 2.1 \times 10^{ -5 }$ & $ 6.5 \times 10^{ 2 }$ \\
... & ... & 0.1 & 400 & 3.3 & $ 6.2 \times 10^{ -3 }$ & $\mathbf{ 5.8 \times 10^{ -3 }}$ \\

@@

\label{table:models}  
\end{tabular}
\begin{tablenotes}
\item $^{(a)}$ Inner power-law index of stellar Nuker profile.
  $^{(b)}$ Break radius of stellar Nuker profile.  $^{(c)}$Accretion
  rate in Eddington units, normalized to a stellar mass input
  parameter $\eta = 0.2$.  $^{(d)}$Ratio of wind heating rate to
  radiative cooling rate at the stagnation radius.  Thermally unstable
  solutions are shown in bold text.  $\dagger$Calculated with
  radiative cooling included, assuming mass loss parameter $\eta =
  0.2$.  $\ddagger$Calculated with radiative cooling and conductivity
  included, assuming mass loss parameter $\eta = 0.2$ and conductivity
  saturation parameter $\phi = 0.1$ (recall that the
  conductive heat flux saturates to $F_{\rm cond}=5\phi \rho c_s^3$). 
\end{tablenotes}
\end{minipage}
\end{threeparttable}

@@

If Compton heating acts alone, i.e. $\tilde{v}_{w} = v_{w}^{C}$, then solving equation
(\ref{eq:vC}) for $\tilde{v}_{\rm w}$ yields
\begin{align} v_{w}^{\rm C} \simeq
  \begin{cases} 160 \eta_{0.02}^{0.23}T_{\rm
C,9}^{0.12}\epsilon_{-2}^{0.23} M_{\bullet,8}^{0.18}\,{\rm km\,s^{-1}}
&, \text{core}\\ 90 \eta_{0.02}^{0.34}T_{\rm
C,9}^{0.17}\epsilon_{-2}^{0.34} M_{\bullet,8}^{0.17}\,{\rm km\,s^{-1}}
&, \text{cusp},
  \end{cases}
  \label{eq:vC2}
\end{align} 
Compton heating can thus be significant in young stellar populations with relatively high mass loss rates, e.g. $v_{w}^{\rm C} \gtrsim 300$ km s$^{-1}$ for $\eta \gtrsim 1$.  The mass accretion rate corresponding to the state where Compton heating limits the average accretion rate is given by substituting equation (\ref{eq:vC2}) into equation (\ref{eq:eddr_analytic}):
\begin{align}
\frac{\dot{M}_{C}}{\dot{M}_{\rm edd}} \approx 
\begin{cases} 3\times 10^{-3} \eta_{0.02}^{0.20}T_{\rm
C,9}^{-0.8}\epsilon_{-2}^{-0.8} M_{\bullet,8}^{0.15}
&, \text{core}\\ 8\times 10^{-4} \eta_{0.02}^{0.30}T_{\rm
C,9}^{-0.7}\epsilon_{-2}^{-0.7} M_{\bullet,8}^{0.14}
&, \text{cusp},
  \end{cases}
  \label{eq:MdotCa}
\end{align}
If the accretion luminosity $\epsilon = 10 \dot{M}/\dot{M}_{\rm edd}$
depends on the Eddington ratio as predicted by some models for
radiatively inefficient accretion flows (\citealt{Narayan&Yi95};
\citealt{Narayan+98}; \citealt{XieYuan:2012a}), then the Compton-limited accretion rate becomes
\begin{align}
\frac{\dot{M}_{C}}{\dot{M}_{\rm edd}} \approx 
\begin{cases} 1.8\times 10^{-2} \eta_{0.02}^{0.12}T_{\rm
C,9}^{-0.44}M_{\bullet,8}^{0.09}
&, \text{core}\\ 8.7\times 10^{-4} \eta_{0.02}^{0.17}T_{\rm
C,9}^{-0.4} M_{\bullet,8}^{0.08}
&, \text{cusp}.
  \end{cases}
  \label{eq:MdotC}
\end{align}
%{\bf  Total efficiency is 10 (mdot/MdotEdd). Everywhere.}

>>>>

  $    10^{ 6 }$ & 300 & 100 & 0.12 & $ 5.1 \times 10^{ -5 }$ & 28 \\
... & 600 & 100 & $ 3.2 \times 10^{ -2 }$ & $ 1.0 \times 10^{ -5 }$ & $ 1.9 \times 10^{ 3 }$ \\
... & 1200 & 100 & $ 7.9 \times 10^{ -3 }$ & $ 1.8 \times 10^{ -6 }$ & $ 7.7 \times 10^{ 4 }$ \\
$    10^{ 7 }$ & 300 & 25 & 0.42 & $ 2.4 \times 10^{ -4 }$ & 7 \\
... & ... & 50 & 0.38 & $ 2.0 \times 10^{ -4 }$ & 4.5 \\
... & ... & 100 & 0.43 & $ 2.4 \times 10^{ -4 }$ & 2.7 \\
... & ... & 200 & 0.47 & $ 2.7 \times 10^{ -4 }$ & $\mathbf{2.1}$ \\
... & ... & 400 & 1.1 & $ 7.0 \times 10^{ -4 }$ & $\mathbf{0.28}$ \\
... & 600 & 25 & $ 8.1 \times 10^{ -2 }$ & $ 3.2 \times 10^{ -5 }$ & $ 6.2 \times 10^{ 2 }$ \\
... & ... & 100 & $ 8.1 \times 10^{ -2 }$ & $ 3.2 \times 10^{ -5 }$ & $ 6.2 \times 10^{ 2 }$ \\
... & 1200 & 100 & $ 2.0 \times 10^{ -2 }$ & $ 6.0 \times 10^{ -6 }$ & $ 2.6 \times 10^{ 4 }$ \\
$    10^{ 8 }$ & 300 & 25 & 0.69 & $ 4.2 \times 10^{ -4 }$ & 5.5 \\
... & ... & 50 & 0.92 & $ 6.0 \times 10^{ -4 }$ & 2 \\
... & ... & 100 & 1.4 & $ 9.5 \times 10^{ -4 }$ & $\mathbf{0.48}$ \\
... & ... & 200 & 2.5 & $ 1.9 \times 10^{ -3 }$ & $\mathbf{ 5.3 \times
  10^{ -2 }}$ \\
...$^{\dagger}$ & 450 & 100 & 1.2 & $ 8.1 \times 10^{ -4 }$ & 2.6 \\
... & 600 & 25 & 0.21 & $ 1.0 \times 10^{ -4 }$ & $ 2.1 \times 10^{ 2 }$ \\
... & ... & 100 & 0.22 & $ 1.1 \times 10^{ -4 }$ & $ 1.7 \times 10^{ 2
}$ \\
...$^{\dagger}$ & ... & 100 & 0.22 & $ 1.1 \times 10^{ -4 }$ & $ 1.6 \times 10^{ 2 }$ \\
...$^{\ddagger}$  & ... & 100 & 0.27 & $ 1.4 \times 10^{ -4 }$ & $ 1.3 \times 10^{ 2
}$ \\
... & ... & 200 & 0.23 & $ 1.1 \times 10^{ -4 }$ & $ 1.6 \times 10^{ 2 }$ \\
... & ... & 400 & 0.23 & $ 1.1 \times 10^{ -4 }$ & $ 1.5 \times 10^{ 2 }$ \\
... & 1200 & 100 & $ 5.0 \times 10^{ -2 }$ & $ 1.8 \times 10^{ -5 }$ & $ 8.3 \times 10^{ 3 }$ \\

@@

  $    10^{ 6 }$ & 600 & 25 & $ 9.4 \times 10^{ -2 }$ & $ 7.4 \times 10^{ -6 }$ & $ 1.1 \times 10^{ 2 }$ \\
... & 1200 & 25 & $ 1.5 \times 10^{ -2 }$ & $ 2.3 \times 10^{ -7 }$ & $ 1.7 \times 10^{ 5 }$ \\
... & ... & 50 & $ 1.5 \times 10^{ -2 }$ & $ 2.3 \times 10^{ -7 }$ & $ 1.7 \times 10^{ 5 }$ \\
... & ... & 100 & $ 1.5 \times 10^{ -2 }$ & $ 2.3 \times 10^{ -7 }$ & $ 1.7 \times 10^{ 5 }$ \\
$    10^{ 7 }$ & 600 & 25 & 0.19 & $ 2.9 \times 10^{ -5 }$ & 79 \\
... & ... & 50 & 0.76 & $ 3.9 \times 10^{ -4 }$ & $\mathbf{ 8.0 \times 10^{ -2 }}$ \\
... & 1200 & 25 & $ 3.9 \times 10^{ -2 }$ & $ 1.4 \times 10^{ -6 }$ & $ 2.9 \times 10^{ 4 }$ \\
... & ... & 50 & $ 4.1 \times 10^{ -2 }$ & $ 1.5 \times 10^{ -6 }$ & $ 2.3 \times 10^{ 4 }$ \\
... & ... & 100 & $ 4.8 \times 10^{ -2 }$ & $ 2.1 \times 10^{ -6 }$ & $ 1.2 \times 10^{ 4 }$ \\
$    10^{ 8 }$ & 600 & 25 & 0.27 & $ 5.7 \times 10^{ -5 }$ & $ 1.0 \times 10^{ 2 }$ \\
... & ... & 50 & 0.46 & $ 1.5 \times 10^{ -4 }$ & 9.4 \\
... & 1200 & 25 & $ 8.5 \times 10^{ -2 }$ & $ 6.1 \times 10^{ -6 }$ & $ 8.2 \times 10^{ 3 }$ \\
... & ... & 50 & $ 9.2 \times 10^{ -2 }$ & $ 7.0 \times 10^{ -6 }$ & $ 6.0 \times 10^{ 3 }$ \\
... & ... & 100 & 0.1 & $ 8.8 \times 10^{ -6 }$ & $ 3.8 \times 10^{ 3 }$ \\
... & ... & 200 & 0.15 & $ 1.7 \times 10^{ -5 }$ & $ 8.0 \times 10^{ 2 }$ \\
... & ... & 400 & 6.8 & $ 2.5 \times 10^{ -2 }$ & $\mathbf{ 3.1 \times 10^{ -4 }}$ \\

@@

\label{table:models}  
\end{tabular}
\begin{tablenotes}
\item $^{(a)}$ Inner power-law index of stellar Nuker profile.
  $^{(b)}$ Break radius of stellar Nuker profile.  $^{(c)}$Accretion
  rate in Eddington units, normalized to a stellar mass input
  parameter $\eta = 0.2$.  $^{(d)}$Ratio of wind heating rate to
  radiative cooling rate at the stagnation radius.  Thermally unstable
  solutions are shown in bold text.  $\dagger$Calculated with
  radiative cooling included, assuming mass loss parameter $\eta =
  0.2$.  $\ddagger$Calculated with radiative cooling and conductivity
  included, assuming mass loss parameter $\eta = 0.2$ and conductivity
  saturation parameter $\phi = 0.1$ (recall that the
  conductive heat flux saturates to $F_{\rm cond}=5\phi \rho c_s^3$). 
\end{tablenotes}
\end{minipage}
\end{threeparttable}

@@

If Compton heating acts alone, i.e. $\tilde{v}_{w} = v_{w}^{C}$, then
solving equation (\ref{eq:vC}) for $\tilde{v}_{\rm w}$ yields
\begin{align} v_{w}^{\rm C} \simeq
  \begin{cases} 140 \eta_{0.02}^{0.21}T_{\rm
C,9}^{0.21}\epsilon_{-2}^{0.21} M_{\bullet,8}^{0.16}\,{\rm km\,s^{-1}}
&, \text{core}\\ 95 \eta_{0.02}^{0.34}T_{\rm
C,9}^{0.29}\epsilon_{-2}^{0.29} M_{\bullet,8}^{0.14}\,{\rm km\,s^{-1}}
&, \text{cusp},
  \end{cases}
  \label{eq:vC2}
\end{align} 
Compton heating can thus be significant in young stellar populations
with relatively high mass loss rates, e.g. $v_{w}^{\rm C} \gtrsim 300$
km s$^{-1}$ for $\eta \gtrsim 1$.  The mass accretion rate
corresponding to the state where Compton heating limits the average
accretion rate is given by substituting equation (\ref{eq:vC2}) into
equation (\ref{eq:eddr_analytic}):
\begin{align}
\frac{\dot{M}_{C}}{\dot{M}_{\rm edd}} \approx 
\begin{cases} 2\times 10^{-3} \eta_{0.02}^{0.2}T_{\rm
C,9}^{-0.8}\epsilon_{-2}^{-0.8} M_{\bullet,8}^{0.16}
&, \text{core}\\ 8\times 10^{-4} \eta_{0.02}^{0.3}T_{\rm
C,9}^{-0.7}\epsilon_{-2}^{-0.7} M_{\bullet,8}^{0.14}
&, \text{cusp},
  \end{cases}
  \label{eq:MdotCa}
\end{align}
If the accretion luminosity $\epsilon = 10 \dot{M}/\dot{M}_{\rm edd}$
depends on the Eddington ratio as predicted by some models for
radiatively inefficient accretion flows (\citealt{Narayan&Yi95};
\citealt{Narayan+98}; \citealt{XieYuan:2012a}), then the Compton-limited accretion rate becomes
\begin{align}
\frac{\dot{M}_{C}}{\dot{M}_{\rm edd}} \approx 
\begin{cases} 1.7\times 10^{-2} \eta_{0.02}^{0.12}T_{\rm
C,9}^{-0.44}M_{\bullet,8}^{0.09}
&, \text{core}\\ 8.6\times 10^{-4} \eta_{0.02}^{0.17}T_{\rm
C,9}^{-0.4} M_{\bullet,8}^{0.08}
&, \text{cusp}.
  \end{cases}
  \label{eq:MdotC}
\end{align}
%{\bf  Total efficiency is 10 (mdot/MdotEdd). Everywhere.}
